---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# U.T.lity <img src="man/figures/logo_ut-lity.svg" align="right" height="139" />

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of U.T.-lity is to provide a collection of tools that allow you to analyse data from user experience and usability tests, assess and track quality, and steer your efforts to get your desired cost-benefit out of your research.


## Installation

You can install the development version of Repo from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SigurdJanson/U.T.-lity")
```


## Example

This is the famous plot showing the ratio between the likelihood of finding usability defects and the sample size. Note: `p.occ` being 31% (i.e. 0.31) is the number which Nielsen & Landauer (1993) introduced in their well-known publication and which led to the even more well-known post in [Nielsens AlertBox (Nielsen, 2000)](https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/).

```{r SampleSizePlot}
library(U.T.lity)
nDefectsPlot(p.occ=c(0.1, 0.2, 0.31, 0.5))
```



## Further Readings

Nielsen, J., & Landauer, T. K. (1993). *A mathematical model of the finding of usability problems*. Proceedings of the INTERACT ’93 and CHI ’93 Conference on Human Factors in Computing Systems, 206–213. https://doi.org/10.1145/169059.169166

Nielsen, J. (2000). Why You Only Need to Test with 5 Users. https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/; accessed 2022-09-09
