---
title: "UT-lity"
author: "Jan Seifert"
citation_package: biblatex
bibliography: UT-lity.bib
link-citations: true
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{UT-lity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(U.T.lity)
```



# Q&A

## Confidence of the Defect Frequency

I have conducted a test with users. I want to use the frequency of the defects that I found in order to assess their severity. But - of course - the frequency in my study is just what my sample shows. What are the the confidence intervals of those defects? 

Call `defectci()`.



## Visualising the Defects Found

I want to visualise the usability defects found for each user in a matrix similar to those used by @Sauro2012a [, table 7.3]. 




# Implementation

## ci-Class for Confidence Intervals

All confidence intervals are stored in an S3 class derived from a data frame. See `?ci_new`.




# References

<div id="refs"></div>
